---
title: "Proportion_Studies_Max_0530"
author: "Lan Tao"
date: "2023-05-30"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE, echo=TRUE}
library(mosaic)
library(ggplot2)
library(dplyr)
library(writexl)
library(haven)
library(readxl)
library(gtable)
require(gridExtra)
library(wesanderson)
```


## read data

```{r}

num_greedy_05_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_11.xlsx")
num_patient_05_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_11.xlsx")

num_greedy_05_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_12.xlsx")
num_patient_05_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_12.xlsx")

num_greedy_05_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_13.xlsx")
num_patient_05_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_13.xlsx")

num_greedy_05_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_14.xlsx")
num_patient_05_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_05_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_11.xlsx")
num_patient_05_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_11.xlsx")

num_greedy_05_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_12.xlsx")
num_patient_05_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_12.xlsx")

num_greedy_05_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_13.xlsx")
num_patient_05_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_13.xlsx")

num_greedy_05_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_14.xlsx")
num_patient_05_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_05_m70_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_11.xlsx")
num_patient_05_m70_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_11.xlsx")

num_greedy_05_m70_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_12.xlsx")
num_patient_05_m70_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_12.xlsx")

num_greedy_05_m70_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_13.xlsx")
num_patient_05_m70_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_13.xlsx")

num_greedy_05_m70_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_14.xlsx")
num_patient_05_m70_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_14.xlsx")

#------------------------------------------------------------------------------------

num_greedy_05_m100_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_11.xlsx")
num_patient_05_m100_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_11.xlsx")

num_greedy_05_m100_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_12.xlsx")
num_patient_05_m100_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_12.xlsx")

num_greedy_05_m100_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_13.xlsx")
num_patient_05_m100_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_13.xlsx")

num_greedy_05_m100_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_14.xlsx")
num_patient_05_m100_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_14.xlsx")


```


```{r}
# write a function to update the dataframe s.t. s=min{n_A/n_B, n_B/n_A}

update_dta<-function(dta){
  new_dta<-dta
  new_dta$prop_2<-new_dta$num_B/new_dta$num_A
  prop_s<-apply(new_dta[,5:6],1,min)
  new_dta$prop_s<-as.double(prop_s)
  new_dta
}

```

## update data

```{r}

num_greedy_05_m30_pr2_11<-update_dta(num_greedy_05_m30_pr2_11)
num_patient_05_m30_pr2_11<-update_dta(num_patient_05_m30_pr2_11)

num_greedy_05_m30_pr2_12<-update_dta(num_greedy_05_m30_pr2_12)
num_patient_05_m30_pr2_12<-update_dta(num_patient_05_m30_pr2_12)

num_greedy_05_m30_pr2_13<-update_dta(num_greedy_05_m30_pr2_13)
num_patient_05_m30_pr2_13<-update_dta(num_patient_05_m30_pr2_13)

num_greedy_05_m30_pr2_14<-update_dta(num_greedy_05_m30_pr2_14)
num_patient_05_m30_pr2_14<-update_dta(num_patient_05_m30_pr2_14)


#------------------------------------------------------------------------------------

num_greedy_05_m50_pr2_11<-update_dta(num_greedy_05_m50_pr2_11)
num_patient_05_m50_pr2_11<-update_dta(num_patient_05_m50_pr2_11)

num_greedy_05_m50_pr2_12<-update_dta(num_greedy_05_m50_pr2_12)
num_patient_05_m50_pr2_12<-update_dta(num_patient_05_m50_pr2_12)

num_greedy_05_m50_pr2_13<-update_dta(num_greedy_05_m50_pr2_13)
num_patient_05_m50_pr2_13<-update_dta(num_patient_05_m50_pr2_13)

num_greedy_05_m50_pr2_14<-update_dta(num_greedy_05_m50_pr2_14)
num_patient_05_m50_pr2_14<-update_dta(num_patient_05_m50_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_05_m70_pr2_11<-update_dta(num_greedy_05_m70_pr2_11)
num_patient_05_m70_pr2_11<-update_dta(num_patient_05_m70_pr2_11)

num_greedy_05_m70_pr2_12<-update_dta(num_greedy_05_m70_pr2_12)
num_patient_05_m70_pr2_12<-update_dta(num_patient_05_m70_pr2_12)

num_greedy_05_m70_pr2_13<-update_dta(num_greedy_05_m70_pr2_13)
num_patient_05_m70_pr2_13<-update_dta(num_patient_05_m70_pr2_13)

num_greedy_05_m70_pr2_14<-update_dta(num_greedy_05_m70_pr2_14)
num_patient_05_m70_pr2_14<-update_dta(num_patient_05_m70_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_05_m100_pr2_11<-update_dta(num_greedy_05_m100_pr2_11)
num_patient_05_m100_pr2_11<-update_dta(num_patient_05_m100_pr2_11)

num_greedy_05_m100_pr2_12<-update_dta(num_greedy_05_m100_pr2_12)
num_patient_05_m100_pr2_12<-update_dta(num_patient_05_m100_pr2_12)

num_greedy_05_m100_pr2_13<-update_dta(num_greedy_05_m100_pr2_13)
num_patient_05_m100_pr2_13<-update_dta(num_patient_05_m100_pr2_13)

num_greedy_05_m100_pr2_14<-update_dta(num_greedy_05_m100_pr2_14)
num_patient_05_m100_pr2_14<-update_dta(num_patient_05_m100_pr2_14)


```




## Part 1 - plot the distribution of s

### 2.1 Greedy algorithm plot

#### 2.1.1 market size m = 30


```{r}
p1 <- ggplot(num_greedy_05_m30_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=30,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m30_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Greedy - m=30,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p3 <- ggplot(num_greedy_05_m30_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=30,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m30_pr2_12,size=0.1) + 
  #ylim(0,5)+
  xlab("Time period")+
  labs(title = "Greedy - m=30,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p5 <- ggplot(num_greedy_05_m30_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=30,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m30_pr2_13,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  #ylim(0,6)+
  labs(title = "Greedy - m=30,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p7 <- ggplot(num_greedy_05_m30_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=30,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()


p8 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m30_pr2_14,size=0.1) + 
  xlab("Time period")+
  labs(title = "Greedy - m=30,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```


#### 2.1.2 market size m = 50

```{r}
p1 <- ggplot(num_greedy_05_m50_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=50,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m50_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Greedy - m=50,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p3 <- ggplot(num_greedy_05_m50_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=50,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m50_pr2_12,size=0.1) + 
  #ylim(0,5)+
  xlab("Time period")+
  labs(title = "Greedy - m=50,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p5 <- ggplot(num_greedy_05_m50_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=50,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m50_pr2_13,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Greedy - m=50,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p7 <- ggplot(num_greedy_05_m50_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=50,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()

p8 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m50_pr2_14,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Greedy - m=50,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```



#### 2.1.3 market size m = 70

```{r}
p1 <- ggplot(num_greedy_05_m70_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=70,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m70_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Greedy - m=70,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p3 <- ggplot(num_greedy_05_m70_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=70,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m70_pr2_12,size=0.1) + 
  #ylim(0,5)+
  xlab("Time period")+
  labs(title = "Greedy - m=70,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p5 <- ggplot(num_greedy_05_m70_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=70,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m70_pr2_13,size=0.1) + 
  ylab("prop")+
  xlab("Time period")+
  labs(title = "Greedy - m=70,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p7 <- ggplot(num_greedy_05_m70_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=70,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()

p8 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m70_pr2_14,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Greedy - m=70,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```


#### 2.1.4 market size m = 100

```{r}
p1 <- ggplot(num_greedy_05_m100_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=100,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_greedy_05_m100_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Greedy - m=100,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p3 <- ggplot(num_greedy_05_m100_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=100,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m100_pr2_12,size=0.1) + 
  #ylim(0,5)+
  ylab("prop")+
  xlab("Time period")+
  labs(title = "Greedy - m=100,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p5 <- ggplot(num_greedy_05_m100_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=100,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m100_pr2_13,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Greedy - m=100,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p7 <- ggplot(num_greedy_05_m100_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Greedy - m=100,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()

p8 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_greedy_05_m100_pr2_14,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Greedy - m=100,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```



### 2.2 Patient algorithm plot

#### 2.2.1 market size m = 30

```{r}
p1 <- ggplot(num_patient_05_m30_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=30,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m30_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Patient - m=30,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p3 <- ggplot(num_patient_05_m30_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=30,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m30_pr2_12,size=0.1) + 
  #ylim(0,5)+
  xlab("Time period")+
  labs(title = "Patient - m=30,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p5 <- ggplot(num_patient_05_m30_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=30,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m30_pr2_13,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  #ylim(0,6)+
  labs(title = "Patient - m=30,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p7 <- ggplot(num_patient_05_m30_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=30,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()


p8 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m30_pr2_14,size=0.1) + 
  xlab("Time period")+
  labs(title = "Patient - m=30,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```



#### 2.2.2 market size m = 50

```{r}
p1 <- ggplot(num_patient_05_m50_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=50,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m50_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Patient - m=50,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p3 <- ggplot(num_patient_05_m50_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=50,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m50_pr2_12,size=0.1) + 
  #ylim(0,5)+
  xlab("Time period")+
  labs(title = "Patient - m=50,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p5 <- ggplot(num_patient_05_m50_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=50,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m50_pr2_13,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Patient - m=50,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p7 <- ggplot(num_patient_05_m50_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=50,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()

p8 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m50_pr2_14,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Patient - m=50,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```



#### 2.2.3 market size m = 70

```{r}
p1 <- ggplot(num_patient_05_m70_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=70,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m70_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Patient - m=70,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 


#-------------------------------------------------------------------------------

p3 <- ggplot(num_patient_05_m70_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=70,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m70_pr2_12,size=0.1) + 
  #ylim(0,5)+
  xlab("Time period")+
  labs(title = "Patient - m=70,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p5 <- ggplot(num_patient_05_m70_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=70,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m70_pr2_13,size=0.1) + 
  ylab("prop")+
  xlab("Time period")+
  labs(title = "Patient - m=70,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p7 <- ggplot(num_patient_05_m70_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=70,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()

p8 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m70_pr2_14,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Patient - m=70,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2 )

```



#### 2.2.4 market size m = 100

```{r}
p1 <- ggplot(num_patient_05_m100_pr2_11[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=100,pa=0.5,T,p1=0.03,p2=0.01,pr=2")+
 theme_bw()

p2 <- ggplot(data = NULL, aes(x = c(1:T), y = prop_s)) + 
  geom_point(data=num_patient_05_m100_pr2_11,size=0.1) + 
  #ylim(0,4)+
  xlab("Time period")+
  labs(title = "Patient - m=100,pa=0.5,T,p1=0.03,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p3 <- ggplot(num_patient_05_m100_pr2_12[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=100,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
 theme_bw()

p4 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m100_pr2_12,size=0.1) + 
  #ylim(0,5)+
  ylab("prop")+
  xlab("Time period")+
  labs(title = "Patient - m=100,pa=0.5,T,p1=0.05,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p5 <- ggplot(num_patient_05_m100_pr2_13[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=100,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
 theme_bw()

p6 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m100_pr2_13,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Patient - m=100,pa=0.5,T,p1=0.1,p2=0.01,pr=2") +
  theme_bw() 

#-------------------------------------------------------------------------------

p7 <- ggplot(num_patient_05_m100_pr2_14[800:1000,], aes(x=prop_s)) + 
 geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666")+
 labs(title = "Patient - m=100,pa=0.5,T,p1=0.8,p2=0.01,pr=2")+
 theme_bw()

p8 <- ggplot(data = NULL, aes(x = c(1:T), y = as.double(prop_s))) + 
  geom_point(data=num_patient_05_m100_pr2_14,size=0.1) + 
  xlab("Time period")+
  ylab("prop")+
  labs(title = "Patient - m=100,pa=0.5,T,p1=0.8,p2=0.01,pr=2") +
  theme_bw() 


grid.arrange(p1,p2,p3,p4,p5,p6,p7,p8,nrow=4,ncol=2)

```




## Findings

+ According to the plot of proportion of $s$, most of the distribution of proportion are all left-skewed distribution. In Patient algorithm, the density plots of proportion are all left-skewed distribution; while in Greedy algorithm, some of the density plot of the proportion could not be plotted due to many inf and 0 values, which indicates that one type agents would often vanish (become zero) under steady state. At this time, the dotplot of proportion would be shown as several horizontal lines, which means the value of proportion is among several fixed values. This case happens only when either compatible probability is rather large or newly coming agents arrive in the market in a higher rate. 

+ Based on these observations, we assume that the distribution of proportion is gamma distribution ~$Beta(\alpha,\beta)$.




## Fitted Beta distribution to $s$


Fit $Beta(\alpha,\beta)$ on the data.

```{r}
# Greedy m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
data <-num_greedy_05_m70_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)


ggplot(num_greedy_05_m70_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=70,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
  theme_bw()

```


```{r}
# Greedy m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
data <-num_greedy_05_m100_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)


ggplot(num_greedy_05_m100_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=100,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
  theme_bw()

```




```{r}
# Patient m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
data <-num_patient_05_m70_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)


ggplot(num_patient_05_m70_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=70,pa=0.5,T,p1=0.05,p2=0.01,pr=2")+
  theme_bw()


```

```{r}
# Patient m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
data <-num_patient_05_m100_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)


ggplot(num_patient_05_m100_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=100,pa=0.5,T,p1=0.1,p2=0.01,pr=2")+
  theme_bw()


```
