---
title: "Fit_Test_Proportion_Studies"
author: "Lan Tao"
date: "2023-10-26"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE, echo=TRUE}
library(mosaic)
library(ggplot2)
library(dplyr)
library(writexl)
library(haven)
library(readxl)
library(gtable)
require(gridExtra)
library(wesanderson)
library(betareg)
# library(cli)
library(fitdistrplus)
library(aods3)
library(cmstatr)
```


## read data

```{r, include=FALSE}

num_greedy_05_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_11.xlsx")
num_patient_05_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_11.xlsx")

num_greedy_05_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_12.xlsx")
num_patient_05_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_12.xlsx")

num_greedy_05_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_13.xlsx")
num_patient_05_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_13.xlsx")

num_greedy_05_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_14.xlsx")
num_patient_05_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_05_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_11.xlsx")
num_patient_05_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_11.xlsx")

num_greedy_05_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_12.xlsx")
num_patient_05_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_12.xlsx")

num_greedy_05_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_13.xlsx")
num_patient_05_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_13.xlsx")

num_greedy_05_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_14.xlsx")
num_patient_05_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_05_m70_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_11.xlsx")
num_patient_05_m70_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_11.xlsx")

num_greedy_05_m70_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_12.xlsx")
num_patient_05_m70_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_12.xlsx")

num_greedy_05_m70_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_13.xlsx")
num_patient_05_m70_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_13.xlsx")

num_greedy_05_m70_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_14.xlsx")
num_patient_05_m70_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_14.xlsx")

#------------------------------------------------------------------------------------

num_greedy_05_m100_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_11.xlsx")
num_patient_05_m100_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_11.xlsx")

num_greedy_05_m100_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_12.xlsx")
num_patient_05_m100_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_12.xlsx")

num_greedy_05_m100_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_13.xlsx")
num_patient_05_m100_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_13.xlsx")

num_greedy_05_m100_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_14.xlsx")
num_patient_05_m100_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_06_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_11.xlsx")
num_patient_06_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_11.xlsx")

num_greedy_06_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_12.xlsx")
num_patient_06_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_12.xlsx")

num_greedy_06_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_13.xlsx")
num_patient_06_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_13.xlsx")

num_greedy_06_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_14.xlsx")
num_patient_06_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_06_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_11.xlsx")
num_patient_06_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_11.xlsx")

num_greedy_06_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_12.xlsx")
num_patient_06_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_12.xlsx")

num_greedy_06_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_13.xlsx")
num_patient_06_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_13.xlsx")

num_greedy_06_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_14.xlsx")
num_patient_06_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_14.xlsx")

```

## update data


```{r, include=FALSE}
# write a function to update the data frame s.t. s=min{n_A/n_B, n_B/n_A}

update_dta<-function(dta){
  new_dta<-dta
  new_dta$prop_2<-new_dta$num_B/new_dta$num_A
  prop_s<-apply(new_dta[,5:6],1,min)
  new_dta$prop_s<-as.double(prop_s)
  new_dta
}

```


```{r, include=FALSE}

num_greedy_05_m30_pr2_11<-update_dta(num_greedy_05_m30_pr2_11)
num_patient_05_m30_pr2_11<-update_dta(num_patient_05_m30_pr2_11)

num_greedy_05_m30_pr2_12<-update_dta(num_greedy_05_m30_pr2_12)
num_patient_05_m30_pr2_12<-update_dta(num_patient_05_m30_pr2_12)

num_greedy_05_m30_pr2_13<-update_dta(num_greedy_05_m30_pr2_13)
num_patient_05_m30_pr2_13<-update_dta(num_patient_05_m30_pr2_13)

num_greedy_05_m30_pr2_14<-update_dta(num_greedy_05_m30_pr2_14)
num_patient_05_m30_pr2_14<-update_dta(num_patient_05_m30_pr2_14)


#------------------------------------------------------------------------------------

num_greedy_05_m50_pr2_11<-update_dta(num_greedy_05_m50_pr2_11)
num_patient_05_m50_pr2_11<-update_dta(num_patient_05_m50_pr2_11)

num_greedy_05_m50_pr2_12<-update_dta(num_greedy_05_m50_pr2_12)
num_patient_05_m50_pr2_12<-update_dta(num_patient_05_m50_pr2_12)

num_greedy_05_m50_pr2_13<-update_dta(num_greedy_05_m50_pr2_13)
num_patient_05_m50_pr2_13<-update_dta(num_patient_05_m50_pr2_13)

num_greedy_05_m50_pr2_14<-update_dta(num_greedy_05_m50_pr2_14)
num_patient_05_m50_pr2_14<-update_dta(num_patient_05_m50_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_05_m70_pr2_11<-update_dta(num_greedy_05_m70_pr2_11)
num_patient_05_m70_pr2_11<-update_dta(num_patient_05_m70_pr2_11)

num_greedy_05_m70_pr2_12<-update_dta(num_greedy_05_m70_pr2_12)
num_patient_05_m70_pr2_12<-update_dta(num_patient_05_m70_pr2_12)

num_greedy_05_m70_pr2_13<-update_dta(num_greedy_05_m70_pr2_13)
num_patient_05_m70_pr2_13<-update_dta(num_patient_05_m70_pr2_13)

num_greedy_05_m70_pr2_14<-update_dta(num_greedy_05_m70_pr2_14)
num_patient_05_m70_pr2_14<-update_dta(num_patient_05_m70_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_05_m100_pr2_11<-update_dta(num_greedy_05_m100_pr2_11)
num_patient_05_m100_pr2_11<-update_dta(num_patient_05_m100_pr2_11)

num_greedy_05_m100_pr2_12<-update_dta(num_greedy_05_m100_pr2_12)
num_patient_05_m100_pr2_12<-update_dta(num_patient_05_m100_pr2_12)

num_greedy_05_m100_pr2_13<-update_dta(num_greedy_05_m100_pr2_13)
num_patient_05_m100_pr2_13<-update_dta(num_patient_05_m100_pr2_13)

num_greedy_05_m100_pr2_14<-update_dta(num_greedy_05_m100_pr2_14)
num_patient_05_m100_pr2_14<-update_dta(num_patient_05_m100_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_06_m30_pr2_11<-update_dta(num_greedy_06_m30_pr2_11)
num_patient_06_m30_pr2_11<-update_dta(num_patient_06_m30_pr2_11)

num_greedy_06_m30_pr2_12<-update_dta(num_greedy_06_m30_pr2_12)
num_patient_06_m30_pr2_12<-update_dta(num_patient_06_m30_pr2_12)

num_greedy_06_m30_pr2_13<-update_dta(num_greedy_06_m30_pr2_13)
num_patient_06_m30_pr2_13<-update_dta(num_patient_06_m30_pr2_13)

num_greedy_06_m30_pr2_14<-update_dta(num_greedy_06_m30_pr2_14)
num_patient_06_m30_pr2_14<-update_dta(num_patient_06_m30_pr2_14)


#------------------------------------------------------------------------------------

num_greedy_06_m50_pr2_11<-update_dta(num_greedy_06_m50_pr2_11)
num_patient_06_m50_pr2_11<-update_dta(num_patient_06_m50_pr2_11)

num_greedy_06_m50_pr2_12<-update_dta(num_greedy_06_m50_pr2_12)
num_patient_06_m50_pr2_12<-update_dta(num_patient_06_m50_pr2_12)

num_greedy_06_m50_pr2_13<-update_dta(num_greedy_06_m50_pr2_13)
num_patient_06_m50_pr2_13<-update_dta(num_patient_06_m50_pr2_13)

num_greedy_06_m50_pr2_14<-update_dta(num_greedy_06_m50_pr2_14)
num_patient_06_m50_pr2_14<-update_dta(num_patient_06_m50_pr2_14)

```


## Greedy Algorithm

### Greedy - group 11 (m=70, pa=0.5, p1=0.05, p2=0.01, pr=2)

```{r}
# Greedy m=70, pa=0.5, p1=0.03, p2=0.01, pr=2
data <- num_greedy_05_m70_pr2_11$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m70_pr2_11[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=70,p1=0.03,p2=0.01")+
  theme_bw()
```


### Greedy - group 12 (m=70, pa=0.5, p1=0.05, p2=0.01, pr=2)

```{r}
# Greedy m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
data <- num_greedy_05_m70_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m70_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=70,p1=0.05,p2=0.01")+
  theme_bw()
```


### Greedy - group 13 (m=70, pa=0.5, p1=0.1, p2=0.01, pr=2)

```{r}
# Greedy m=70, pa=0.5, p1=0.1, p2=0.01, pr=2
data <- num_greedy_05_m70_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)


# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m70_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=70,p1=0.1,p2=0.01")+
  theme_bw()
```


### Greedy - group 14 (m=70, pa=0.5, p1=0.8, p2=0.01, pr=2)

```{r}
# Greedy m=70, pa=0.5, p1=0.8, p2=0.01, pr=2
data <- num_greedy_05_m70_pr2_14$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m70_pr2_14[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=70,p1=0.8,p2=0.01")+
  theme_bw()
```



### Greedy - group 21 (m=100, pa=0.5, p1=0.03, p2=0.01, pr=2)

```{r}
# Greedy m=100, pa=0.5, p1=0.03, p2=0.01, pr=2
data <- num_greedy_05_m100_pr2_11$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m100_pr2_11[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=100,p1=0.03,p2=0.01")+
  theme_bw()
```


### Greedy - group 22 (m=100, pa=0.5, p1=0.05, p2=0.01, pr=2)

```{r}
# Greedy m=100, pa=0.5, p1=0.05, p2=0.01, pr=2
data <- num_greedy_05_m100_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m100_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=100,p1=0.05,p2=0.01")+
  theme_bw()
```

### Greedy - group 23 (m=100, pa=0.5, p1=0.1, p2=0.01, pr=2)

```{r}
# Greedy m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
data <- num_greedy_05_m100_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m100_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=100,p1=0.1,p2=0.01")+
  theme_bw()
```


### Greedy - group 24 (m=100, pa=0.5, p1=0.8, p2=0.01, pr=2)

```{r}
# Greedy m=100, pa=0.5, p1=0.8, p2=0.01, pr=2
data <- num_greedy_05_m100_pr2_14$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m100_pr2_14[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=100,p1=0.8,p2=0.01")+
  theme_bw()
```

### Patient - group 11 (m=70, pa=0.5, p1=0.03, p2=0.01, pr=2)

```{r}
# Patient m=70, pa=0.5, p1=0.03, p2=0.01, pr=2
data <- num_patient_05_m70_pr2_11$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_patient_05_m70_pr2_11[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=70,p1=0.03,p2=0.01")+
  theme_bw()
```
### Patient - group 12 (m=70, pa=0.5, p1=0.05, p2=0.01, pr=2)

```{r}
# Patient m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
data <- num_patient_05_m70_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_patient_05_m70_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=70,p1=0.05,p2=0.01")+
  theme_bw()
```

### Patient - group 13 (m=70, pa=0.5, p1=0.1, p2=0.01, pr=2)

```{r}
# Patient m=70, pa=0.5, p1=0.1, p2=0.01, pr=2
data <- num_patient_05_m70_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_patient_05_m70_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=70,p1=0.1,p2=0.01")+
  theme_bw()
```

### Patient - group 14 (m=70, pa=0.8, p1=0.03, p2=0.01, pr=2)

```{r}
# Patient m=70, pa=0.5, p1=0.8, p2=0.01, pr=2
data <- num_patient_05_m70_pr2_14$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_patient_05_m70_pr2_14[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=70,p1=0.8,p2=0.01")+
  theme_bw()
```

### Patient - group 21 (m=100, pa=0.5, p1=0.05, p2=0.01, pr=2)

```{r}
# Patient m=100, pa=0.5, p1=0.05, p2=0.01, pr=2
data <- num_patient_05_m100_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_patient_05_m100_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=100,p1=0.05,p2=0.01")+
  theme_bw()
```


### Patient - group 22 (m=100, pa=0.5, p1=0.05, p2=0.01, pr=2)

```{r}
# Patient m=100, pa=0.5, p1=0.05, p2=0.01, pr=2
data <- num_patient_05_m100_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

### Kolmogorov-Smirnov Tests
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(x_1, "pbeta", alpha, beta)
# ks.test(x_1, x_2)

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_patient_05_m100_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=100,p1=0.05,p2=0.01")+
  theme_bw()
```




### ---------------------------------------------------------


### Plot - group 1 
```{r}
# Greedy m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
data <-num_greedy_05_m70_pr2_12$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

ggplot(num_greedy_05_m70_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=70,p1=0.05,p2=0.01")+
  theme_bw()
```


### Plot - group 2

```{r}
# Greedy m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
data <-num_greedy_05_m100_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)


ggplot(num_greedy_05_m100_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Greedy - m=100,p1=0.1,p2=0.01")+
  theme_bw()

```


### Kolmogorov-Smirnov Tests

```{r}
# x_1 <- data
# x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(data, "pbeta", alpha, beta)
```

## Patient Algorithm

### Plot - group 1 

```{r}
# Patient m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
data <-num_patient_05_m70_pr2_12$prop_s

exp_s <- mean(data[500:1000], na.rm = TRUE)
var_s <- var(data[500:1000], na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

# Visual Inspection
ggplot(num_patient_05_m70_pr2_12[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=70,p1=0.05,p2=0.01")+
  theme_bw()

```

### Kolmogorov-Smirnov Tests - group 1 

```{r}
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

# ks.test(data, "pbeta", alpha, beta)
ks.test(x_1, x_2)


```




### Plot - group 2
```{r}
# Patient m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
data <-num_patient_05_m100_pr2_13$prop_s

exp_s<-mean(data[500:1000], na.rm = TRUE)
var_s<-var(data[500:1000],na.rm = TRUE)

alpha = exp_s*(exp_s*(1-exp_s)/var_s-1)
beta  = (1-exp_s)*(exp_s*(1-exp_s)/var_s-1)

alpha
beta

# plot the beta distribution gamma(alpha, beta)

x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x,shape1=alpha,shape2=beta)

fitted_data<-data.frame(x,fitted_val)

# Visual Inspection
ggplot(num_patient_05_m100_pr2_13[800:1000,], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=100,p1=0.1,p2=0.01")+
  theme_bw()

```

### Kolmogorov-Smirnov Tests - group 2
```{r}
x_1 <- data
x_2 <- rbeta(n = 501, shape1 = alpha, shape2 = beta)

ks.test(data, "pbeta", alpha, beta)
# ks.test(x_1, x_2)
```

K-S test problems: the true $\alpha$ and $\beta$ values are unknown, and the $\alpha$ and $\beta$ values that we put into the K-S test are MLE from data, so the results of the above goodness of fit test demonstrates that the density of data does not follow beta distribution with the parameters $\alpha_{MLE}$ and $\beta_{MLE}$.

If we do know the true values of $\alpha$ and $\beta$, then the log-likelihood would be exactly following $\chi^2$ distribution; if we don't know the true values of $\alpha$ and $\beta$, and we replace them with MLE, then the distribution of log-likelihood would not be $\chi^2$ distribution. So we need to examine how good the distribution is close to $\chi^2$ distribution.




