---
title: "Fit_Test_Proportion_Studies"
author: "Lan Tao"
date: "2023-12-05"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r include=FALSE, echo=TRUE}
library(mosaic)
library(ggplot2)
library(dplyr)
library(writexl)
library(haven)
library(readxl)

# library(cli)
library(cmstatr)
library(EnvStats)
library(ddst)
```


## read simulation data
```{r reading-data, include=FALSE}

num_greedy_05_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_11.xlsx")
num_patient_05_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_11.xlsx")

num_greedy_05_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_12.xlsx")
num_patient_05_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_12.xlsx")

num_greedy_05_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_13.xlsx")
num_patient_05_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_13.xlsx")

num_greedy_05_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m30_pr2_14.xlsx")
num_patient_05_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m30_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_05_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_11.xlsx")
num_patient_05_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_11.xlsx")

num_greedy_05_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_12.xlsx")
num_patient_05_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_12.xlsx")

num_greedy_05_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_13.xlsx")
num_patient_05_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_13.xlsx")

num_greedy_05_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m50_pr2_14.xlsx")
num_patient_05_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m50_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_05_m70_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_11.xlsx")
num_patient_05_m70_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_11.xlsx")

num_greedy_05_m70_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_12.xlsx")
num_patient_05_m70_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_12.xlsx")

num_greedy_05_m70_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_13.xlsx")
num_patient_05_m70_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_13.xlsx")

num_greedy_05_m70_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m70_pr2_14.xlsx")
num_patient_05_m70_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m70_pr2_14.xlsx")

#------------------------------------------------------------------------------------

num_greedy_05_m100_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_11.xlsx")
num_patient_05_m100_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_11.xlsx")

num_greedy_05_m100_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_12.xlsx")
num_patient_05_m100_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_12.xlsx")

num_greedy_05_m100_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_13.xlsx")
num_patient_05_m100_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_13.xlsx")

num_greedy_05_m100_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_05_m100_pr2_14.xlsx")
num_patient_05_m100_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_05_m100_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_06_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_11.xlsx")
num_patient_06_m50_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_11.xlsx")

num_greedy_06_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_12.xlsx")
num_patient_06_m50_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_12.xlsx")

num_greedy_06_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_13.xlsx")
num_patient_06_m50_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_13.xlsx")

num_greedy_06_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m50_pr2_14.xlsx")
num_patient_06_m50_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m50_pr2_14.xlsx")


#------------------------------------------------------------------------------------

num_greedy_06_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_11.xlsx")
num_patient_06_m30_pr2_11<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_11.xlsx")

num_greedy_06_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_12.xlsx")
num_patient_06_m30_pr2_12<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_12.xlsx")

num_greedy_06_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_13.xlsx")
num_patient_06_m30_pr2_13<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_13.xlsx")

num_greedy_06_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_greedy_06_m30_pr2_14.xlsx")
num_patient_06_m30_pr2_14<-read_excel("~/Desktop/Matching Market/Simulation/Simulation_0510/Simulation_Result_Data/num_patient_06_m30_pr2_14.xlsx")

```

## update data
```{r update-data-func, include=FALSE}
# write a function to update the data frame s.t. s=min{n_A/n_B, n_B/n_A}

update_dta<-function(dta){
  new_dta<-dta
  new_dta$prop_2<-new_dta$num_B/new_dta$num_A
  prop_s<-apply(new_dta[,5:6],1,min)
  new_dta$prop_s<-as.double(prop_s)
  new_dta
}

```

```{r updating-data, include=FALSE}

num_greedy_05_m30_pr2_11<-update_dta(num_greedy_05_m30_pr2_11)
num_patient_05_m30_pr2_11<-update_dta(num_patient_05_m30_pr2_11)

num_greedy_05_m30_pr2_12<-update_dta(num_greedy_05_m30_pr2_12)
num_patient_05_m30_pr2_12<-update_dta(num_patient_05_m30_pr2_12)

num_greedy_05_m30_pr2_13<-update_dta(num_greedy_05_m30_pr2_13)
num_patient_05_m30_pr2_13<-update_dta(num_patient_05_m30_pr2_13)

num_greedy_05_m30_pr2_14<-update_dta(num_greedy_05_m30_pr2_14)
num_patient_05_m30_pr2_14<-update_dta(num_patient_05_m30_pr2_14)


#------------------------------------------------------------------------------------

num_greedy_05_m50_pr2_11<-update_dta(num_greedy_05_m50_pr2_11)
num_patient_05_m50_pr2_11<-update_dta(num_patient_05_m50_pr2_11)

num_greedy_05_m50_pr2_12<-update_dta(num_greedy_05_m50_pr2_12)
num_patient_05_m50_pr2_12<-update_dta(num_patient_05_m50_pr2_12)

num_greedy_05_m50_pr2_13<-update_dta(num_greedy_05_m50_pr2_13)
num_patient_05_m50_pr2_13<-update_dta(num_patient_05_m50_pr2_13)

num_greedy_05_m50_pr2_14<-update_dta(num_greedy_05_m50_pr2_14)
num_patient_05_m50_pr2_14<-update_dta(num_patient_05_m50_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_05_m70_pr2_11<-update_dta(num_greedy_05_m70_pr2_11)
num_patient_05_m70_pr2_11<-update_dta(num_patient_05_m70_pr2_11)

num_greedy_05_m70_pr2_12<-update_dta(num_greedy_05_m70_pr2_12)
num_patient_05_m70_pr2_12<-update_dta(num_patient_05_m70_pr2_12)

num_greedy_05_m70_pr2_13<-update_dta(num_greedy_05_m70_pr2_13)
num_patient_05_m70_pr2_13<-update_dta(num_patient_05_m70_pr2_13)

num_greedy_05_m70_pr2_14<-update_dta(num_greedy_05_m70_pr2_14)
num_patient_05_m70_pr2_14<-update_dta(num_patient_05_m70_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_05_m100_pr2_11<-update_dta(num_greedy_05_m100_pr2_11)
num_patient_05_m100_pr2_11<-update_dta(num_patient_05_m100_pr2_11)

num_greedy_05_m100_pr2_12<-update_dta(num_greedy_05_m100_pr2_12)
num_patient_05_m100_pr2_12<-update_dta(num_patient_05_m100_pr2_12)

num_greedy_05_m100_pr2_13<-update_dta(num_greedy_05_m100_pr2_13)
num_patient_05_m100_pr2_13<-update_dta(num_patient_05_m100_pr2_13)

num_greedy_05_m100_pr2_14<-update_dta(num_greedy_05_m100_pr2_14)
num_patient_05_m100_pr2_14<-update_dta(num_patient_05_m100_pr2_14)

#------------------------------------------------------------------------------------

num_greedy_06_m30_pr2_11<-update_dta(num_greedy_06_m30_pr2_11)
num_patient_06_m30_pr2_11<-update_dta(num_patient_06_m30_pr2_11)

num_greedy_06_m30_pr2_12<-update_dta(num_greedy_06_m30_pr2_12)
num_patient_06_m30_pr2_12<-update_dta(num_patient_06_m30_pr2_12)

num_greedy_06_m30_pr2_13<-update_dta(num_greedy_06_m30_pr2_13)
num_patient_06_m30_pr2_13<-update_dta(num_patient_06_m30_pr2_13)

num_greedy_06_m30_pr2_14<-update_dta(num_greedy_06_m30_pr2_14)
num_patient_06_m30_pr2_14<-update_dta(num_patient_06_m30_pr2_14)


#------------------------------------------------------------------------------------

num_greedy_06_m50_pr2_11<-update_dta(num_greedy_06_m50_pr2_11)
num_patient_06_m50_pr2_11<-update_dta(num_patient_06_m50_pr2_11)

num_greedy_06_m50_pr2_12<-update_dta(num_greedy_06_m50_pr2_12)
num_patient_06_m50_pr2_12<-update_dta(num_patient_06_m50_pr2_12)

num_greedy_06_m50_pr2_13<-update_dta(num_greedy_06_m50_pr2_13)
num_patient_06_m50_pr2_13<-update_dta(num_patient_06_m50_pr2_13)

num_greedy_06_m50_pr2_14<-update_dta(num_greedy_06_m50_pr2_14)
num_patient_06_m50_pr2_14<-update_dta(num_patient_06_m50_pr2_14)

```

```{r helper-func}
## helper function
visual <- function(dataset, alpha, beta){
  x <- seq(0,1,by=0.001)
  fitted_val <- dbeta(x, shape1=alpha, shape2=beta)
  fitted_data <- data.frame(x, fitted_val)
  g <- ggplot(dataset, aes(x=prop_s)) +
    geom_histogram(aes(y=..density..), colour="black", fill="white")+
    geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
    geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue", size=0.1, show.legend = TRUE)+
    # labs(title = "Patient - m=100, p1=0.03, p2=0.01")+
    theme_bw()
  return(g)
}

# g <- visual(num_patient_05_m100_pr2_11[501:1000, ], alpha_star, beta_star)
# g + labs(title = "Patient - m=100, p1=0.03, p2=0.01")
```


## Hypothesis test
$$
H_0: \text{ Beta CDF (s) is following unif(0,1)} \\
H_0: \text{ Beta CDF (s) is not following unif(0,1)}
$$



##
```{r test, include=FALSE}
z = rexp(80,4)
ddst.exp.test(z, compute.p = TRUE)

z = rbeta(80, shape1 = 7.6, shape2 = 1.2)
# histogram(z)
ddst.exp.test(z, compute.p = TRUE)
```


```{r example, include=FALSE}
# example
# Patient m=100, pa=0.5, p1=0.03, p2=0.01, pr=2
data <- num_patient_05_m100_pr2_11$prop_s[501:1000]
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 


par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# Visual inspection
x <- seq(0,1,by=0.001)
fitted_val <- dbeta(x, shape1=alpha_star, shape2=beta_star)

fitted_data <- data.frame(x, fitted_val)

ggplot(num_patient_05_m100_pr2_11[501:1000, ], aes(x=prop_s)) +
  geom_histogram(aes(y=..density..), colour="black", fill="white")+
  geom_density(alpha=.2, colour="palevioletred1",fill="palevioletred1")+
  geom_point(data = fitted_data, aes(x = x, y = fitted_val), colour = "cornflowerblue",size=0.1,show.legend = TRUE)+
  labs(title = "Patient - m=100,p1=0.03,p2=0.01")+
  theme_bw()


# construct the empirical distribution
# Bootstrap sampling
M <- 1000  # the number of bootstrap
alpha_emp <- numeric(M)
beta_emp <- numeric(M)
T_emp <- numeric(M)

set.seed(156)
for (i in 1:M) {
  boot_s <- rbeta(n, shape1 = alpha_star, shape2 = beta_star)
  par_emp <- ebeta(boot_s, method = "mle") 
  alpha_emp[i] <- as.numeric(par_emp$parameters[1])
  beta_emp[i] <- as.numeric(par_emp$parameters[2]) 
  cdf <- numeric(n)
  for (j in 1:n) {
    s <- boot_s[j]
    cdf[j] <- (pbeta(s, shape1 = alpha_emp[i], shape2 = beta_emp[i]))
  }
  T_emp[i] <- sum(cdf)/n
}

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

histogram(T_emp)

# the observed statistics
cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}
T_obs <- sum(cdf_obs)/n
print(paste("The observed statistics is", T_obs)) 


histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

```


## Data from Patient algorithm
### Patient - group 11 (m=70, pa=0.5, p1=0.03, p2=0.01, pr=2)
```{r}
# Patient m=70, pa=0.5, p1=0.03, p2=0.01, pr=2
dataset <- num_patient_05_m70_pr2_11[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=70, p1=0.03, p2=0.01")

```


### Patient - group 12 (m=70, pa=0.5, p1=0.05, p2=0.01, pr=2)
```{r}
# Patient m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
dataset <- num_patient_05_m70_pr2_12[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)


g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=70, p1=0.05, p2=0.01")

```


### Patient - group 13 (m=70, pa=0.5, p1=0.1, p2=0.01, pr=2)
```{r}
# Patient m=70, pa=0.5, p1=0.1, p2=0.01, pr=2
dataset <- num_patient_05_m70_pr2_13[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)


g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=70, p1=0.1, p2=0.01")

```



### Patient - group 14 (m=70, pa=0.5, p1=0.8, p2=0.01, pr=2)
```{r}
# Patient m=70, pa=0.5, p1=0.8, p2=0.01, pr=2
dataset <- num_patient_05_m70_pr2_14[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)


g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=70, p1=0.8, p2=0.01")

```






### Patient - group 21 (m=100, pa=0.5, p1=0.03, p2=0.01, pr=2)
```{r}
# Patient m=100, pa=0.5, p1=0.03, p2=0.01, pr=2
dataset <- num_patient_05_m100_pr2_11[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)


g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=100, p1=0.03, p2=0.01")

```



### Patient - group 22 (m=100, pa=0.5, p1=0.05, p2=0.01, pr=2)
```{r}
# Patient m=100, pa=0.5, p1=0.05, p2=0.01, pr=2
dataset <- num_patient_05_m100_pr2_12[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
# chi_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
  # chi_obs[i] <- -2*log(cdf_obs[i])
}

histogram(cdf_obs)
# histogram(chi_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=100, p1=0.05, p2=0.01")

```



### Patient - group 23 (m=100, pa=0.5, p1=0.1, p2=0.01, pr=2)
```{r}
# Patient m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
dataset <- num_patient_05_m100_pr2_13[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)


g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=100, p1=0.1, p2=0.01")

```




### Patient - group 24 (m=100, pa=0.5, p1=0.8, p2=0.01, pr=2)
```{r}
# Patient m=100, pa=0.5, p1=0.8, p2=0.01, pr=2
dataset <- num_patient_05_m100_pr2_14[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Patient - m=100, p1=0.8, p2=0.01")

```



## Data from Greedy algorithm

### Remark: We guess the goodness of fit test would not be good from the visual inspection

### Greedy - group 11 (m=70, pa=0.5, p1=0.03, p2=0.01, pr=2)
```{r}
# Greedy m=70, pa=0.5, p1=0.03, p2=0.01, pr=2
dataset <- num_greedy_05_m70_pr2_11[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)
g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=70, p1=0.03, p2=0.01")

```

### Greedy - group 12 (m=70, pa=0.5, p1=0.05, p2=0.01, pr=2)
```{r}
# Greedy m=70, pa=0.5, p1=0.05, p2=0.01, pr=2
dataset <- num_greedy_05_m70_pr2_12[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=70, p1=0.05, p2=0.01")
```

### Greedy - group 13 (m=70, pa=0.5, p1=0.1, p2=0.01, pr=2)

#### warning: there are inf values in this situation
```{r}
# Greedy m=70, pa=0.5, p1=0.1, p2=0.01, pr=2
dataset <- num_greedy_05_m70_pr2_13[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=70, p1=0.1, p2=0.01")
```
### Greedy - group 14 (m=70, pa=0.5, p1=0.8, p2=0.01, pr=2)

#### warning: there are inf values in this situation; apparently the distribution of s concentrated on $\{0, 0.5, 1\}$.
```{r}
# Greedy m=70, pa=0.5, p1=0.8, p2=0.01, pr=2
dataset <- num_greedy_05_m70_pr2_14[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
# ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=70, p1=0.8, p2=0.01")
```



### Greedy - group 21 (m=100, pa=0.5, p1=0.03, p2=0.01, pr=2)
```{r}
# Greedy m=100, pa=0.5, p1=0.03, p2=0.01, pr=2
dataset <- num_greedy_05_m100_pr2_11[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)
g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=100, p1=0.03, p2=0.01")

```


### Greedy - group 22 (m=100, pa=0.5, p1=0.05, p2=0.01, pr=2)
```{r}
# Greedy m=100, pa=0.5, p1=0.05, p2=0.01, pr=2
dataset <- num_greedy_05_m100_pr2_12[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=100, p1=0.05, p2=0.01")

```



### Greedy - group 23 (m=100, pa=0.5, p1=0.1, p2=0.01, pr=2)
#### warning: there are inf values in this situation
```{r}
# Greedy m=100, pa=0.5, p1=0.1, p2=0.01, pr=2
dataset <- num_greedy_05_m100_pr2_13[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- pbeta(s, shape1 = alpha_star, shape2 = beta_star)
}

histogram(cdf_obs)
ddst.uniform.test(cdf_obs, compute.p = TRUE)
g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=100, p1=0.1, p2=0.01")

```


### Greedy - group 24 (m=100, pa=0.5, p1=0.8, p2=0.01, pr=2)
#### warning: there are inf values in this situation
```{r}
# Greedy m=100, pa=0.5, p1=0.8, p2=0.01, pr=2
dataset <- num_greedy_05_m100_pr2_14[501:1000,]
data <- dataset$prop_s
n <- length(data)
eff_n <- sum(!is.na(data)) # the number of non-na elements
print(paste("The number of non-na elements is",eff_n)) 

par <- ebeta(data, method = "mle") # the warning may come from the fact that several values = 1
# ebeta(data[500:1000], method = "mme")
alpha_star <- as.numeric(par$parameters[1])
beta_star <- as.numeric(par$parameters[2])
print(paste("The mle estimator for alpha = ", alpha_star, "beta =", beta_star)) 

# histogram(alpha_emp)
# histogram(beta_emp)
# mean(alpha_emp)
# alpha_star
# mean(beta_emp)
# beta_star

cdf_obs <- numeric(n)
for (i in 1:n){
  s <- data[i]
  cdf_obs[i] <- (pbeta(s, shape1 = alpha_star, shape2 = beta_star))
}

histogram(cdf_obs)
# ddst.uniform.test(cdf_obs, compute.p = TRUE)

g <- visual(dataset, alpha_star, beta_star)
g + labs(title = "Greedy - m=100, p1=0.8, p2=0.01")

```





